\textbf{Code exploration}

### 2024-12-04 paper_Roychoudhury_code.Rnw
Update paper_Roychoudhury_code.Rnw

plot( 1:(n.min+15), post.crit[1:(n.min+15)], type="p", xaxs="i", xlab="n",
        ylab="pr(p>NV)",xlim = c(0,n.min+20), ylim=c(0.5,1),
        lwd=1, pch = ifelse(post.crit.index,16,1),
        main="prob(p>NV) as a function of n", cex.lab=1.4, cex.main=1.4)
  abline(h=p.positive, lty=2)
  abline(v=n.min, lty=3)
  text(1.05*n.min, 0.6, paste("n.min=",n.min, sep=''),adj=0)

@@

nM <-  SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, 
                      dec.value = 0.175, a = alpha_result, b=1,
                      post.est = "median")
nM$n.min # is still 22
@
\end{center}
Additionally, we explore how the minimum sample size changes according to different values of $\alpha$. The below plot gives the relationship between them.
\begin{center}
<<prior_sample_size2, fig.show='asis', echo=FALSE>>=
# Next plot the minimum sample size VS alpha

alpha_vector <- seq(0.005,1,0.005)
# n_min_vector <- rep(0, length(alpha_vector))
# for (i in 1:length(alpha_vector)){
#   a <- alpha_vector[i]
#   n <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, 
#                       dec.value = 0.175, a = a, b=1,
#                       post.est = "median")
#   n_min_vector[i] <- n$n.min[[1]]
# }
# n_min_vector

n_min_vector_stored <- c(21,21,21,21,21,21,21,21,21,21,21,21,21,21,21,
                         22,22,22,22,22,22,22,22,22,22,22,22,22,22,22, 
                         22,22,22,22,22,22,22,22,22,22,22,22,22,22,22,
                         22,22,22,22,22,22,22,22,22,17,17,17,23,23,23,
                         23,23,23,23,23,23,23,23,23,23,23,23,23,23,23,
                         23,23,23,23,23,23,23,17,17,17,17,17,18,18,18,
                         18,18,18,18,18,18,18,18,18,18,24,24,24,24,24,
                         24,24,24,24,24,18,18,18,18,18,18,18,18,18,18,
                         18,18,18,18,18,18,18,18,18,18,19,19,19,19,19,
                         19,19,19,19,19,19,19,19,19,19,19,19,19,19,19, 
                         19,19,19,19,19,19,19,19,19,19,19,19,19,19,19,
                         19,19,19,19,19,19,19,20,20,20,20,20,20,20,20,
                         20,20,20,20,20,20,20,20,20,20,20,20,20,20,20,
                         20,20,20,20,20)
plot(alpha_vector,n_min_vector_stored, type="l",
     xlab="alpha", ylab="n_min", las=1)
@
\end{center}

@@

<<Table_4, echo=FALSE, results='asis'>>=
kable(subtable_1, format = "latex", booktabs = TRUE, escape = FALSE,
      caption = "1. Dual-criterion design: $\\alpha=0.1$, DV=0.7, n=70") %>%
  kable_styling(latex_options = c("hold_position", "striped")) %>%
  cat()
kable(subtable_2, format = "latex", booktabs = TRUE, escape = FALSE,
      caption = "2. Dual-criterion design: $\\alpha=0.1$, DV=0.7, n=52") %>%
  kable_styling(latex_options = c("hold_position", "striped")) %>%
  cat()
kable(subtable_3, format = "latex", booktabs = TRUE, escape = FALSE,
      caption = "3. Three-outcome design: $n=27$") %>%
  kable_styling(latex_options = c("hold_position", "striped")) %>%
  cat()
@
\pagebreak
%% References
\bibliographystyle{apalike}
\bibliography{bibliography}

>>>>

plot( 1:(n.min+15), post.crit[1:(n.min+15)], type="p", xaxs="i", xlab="n",
        ylab="pr(p>NV)",xlim = c(0,n.min+20), ylim=c(0.5,1),
        lwd=1, pch = ifelse(post.crit.index,16,1),
        main="prob(p>NV) as a function of n", cex.lab=1.4, cex.main=1.4)
  abline(h=p.positive, lty=2)
  abline(v=n.min, lty=3)
  text(1.05*n.min, 0.6, paste("n.min=",n.min, sep=''),adj=0)
  text(30, 0.8, paste("a=",round(a,4)))

@@

nM <-  SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, 
                      dec.value = 0.175, a = alpha_result, b=1,
                      post.est = "median")
nM$n.min # is still 22

@
\end{center}
Additionally, we explore how the minimum sample size changes according to different values of $\alpha$. The below plot gives the relationship between them.
\begin{center}
<<prior_sample_size2, fig.show='asis', echo=FALSE>>=
# Next plot the minimum sample size VS alpha

# alpha_vector <- seq(0.1,1,0.1)
# n_min_vector <- rep(0, length(alpha_vector))
# par(mfrow=c(1,1))
# for (i in 1:length(alpha_vector)){
#   a <- alpha_vector[i]
#   n <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95,
#                       dec.value = 0.175, a = a, b=1,
#                       post.est = "median")
#   n_min_vector[i] <- n$n.min[[1]]
# }
# n_min_vector
# 
# 
alpha_vector <- seq(0.005,1,0.005)
n_min_vector_stored <- c(21,21,21,21,21,21,21,21,21,21,21,21,21,21,21,
                         22,22,22,22,22,22,22,22,22,22,22,22,22,22,22,
                         22,22,22,22,22,22,22,22,22,22,22,22,22,22,22,
                         22,22,22,22,22,22,22,22,22,17,17,17,23,23,23,
                         23,23,23,23,23,23,23,23,23,23,23,23,23,23,23,
                         23,23,23,23,23,23,23,17,17,17,17,17,18,18,18,
                         18,18,18,18,18,18,18,18,18,18,24,24,24,24,24,
                         24,24,24,24,24,18,18,18,18,18,18,18,18,18,18,
                         18,18,18,18,18,18,18,18,18,18,19,19,19,19,19,
                         19,19,19,19,19,19,19,19,19,19,19,19,19,19,19,
                         19,19,19,19,19,19,19,19,19,19,19,19,19,19,19,
                         19,19,19,19,19,19,19,20,20,20,20,20,20,20,20,
                         20,20,20,20,20,20,20,20,20,20,20,20,20,20,20,
                         20,20,20,20,20)
plot(alpha_vector,n_min_vector_stored, type="l",
     xlab="alpha", ylab="n_min", las=1)
@
\end{center}

@@

<<Table_4, echo=FALSE, results='asis'>>=
kable(subtable_1, format = "latex", booktabs = TRUE, escape = FALSE,
      caption = "1. Dual-criterion design: $\\alpha=0.1$, DV=0.7, n=70") %>%
  kable_styling(latex_options = c("hold_position", "striped")) %>%
  cat()
kable(subtable_2, format = "latex", booktabs = TRUE, escape = FALSE,
      caption = "2. Dual-criterion design: $\\alpha=0.1$, DV=0.7, n=52") %>%
  kable_styling(latex_options = c("hold_position", "striped")) %>%
  cat()
kable(subtable_3, format = "latex", booktabs = TRUE, escape = FALSE,
      caption = "3. Three-outcome design: $n=27$") %>%
  kable_styling(latex_options = c("hold_position", "striped")) %>%
  cat()
@
\pagebreak
%% References
\appendix

<<appendix1, fig.width=5, echo=TRUE, results='hide'>>=
n1 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.1, b=1, post.est = "median")
n2 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.2, b=1, post.est = "median")
n3 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.3, b=1, post.est = "median")
n4 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.4, b=1, post.est = "median")
n5 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.5, b=1, post.est = "median")
n6 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.6, b=1, post.est = "median")
n7 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.7, b=1, post.est = "median")
n8 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.8, b=1, post.est = "median")
n9 <- SS_DC_BayesBin(null.value = 0.075, p.positive = 0.95, dec.value = 0.175, 
               a = 0.9, b=1, post.est = "median")
@
\bibliographystyle{apalike}
\bibliography{bibliography}
